Equivalent Income

### 2023-04-27 minos/validation/equivalent_income_checks.Rmd
Changed the utils script to separate out the datain utilities (now in own script). Also changed some function names in the new utils_datain script to be more obvious as to their purpose (some docstring style stuff in there too). Added a new script for testing out some new outcomes visualisations, in standard_deviation_change_SF12.Rmd. More to come

require(tidyverse)
require(ggplot2)

@@

##

>>>>

require(tidyverse)
require(ggplot2)
require(readxl)
require(stringr)

@@

## Adapting Chris' Spreadsheet

```{r}
# Want to remove the one-hot encoding but finding it very difficult in Python

df <- read_excel(path = 'EI_calculation.xlsx')
```

```{r}
df2 <- df %>%
  pivot_longer(cols = phy1:lone3,
               names_to = 'variable',
               values_to = 'level')
```

```{r}
df3 <- df %>%
  pivot_longer(cols = -c(pidp, i_hidp, dis_hcost, hh_size, Yc, EI)) %>%
  filter(value > 0) %>%
  mutate(level = readr::parse_number(as.character(name)))

df3$name <- gsub("\\d+", "", df3$name)

df3 <- df3 %>% 
  select(-value) %>%
  pivot_wider(names_from = 'name',
              values_from = 'level') %>%
  rename(S7_physical_health = phy,
         S7_mental_health = men,
         loneliness = lone,
         S7_labour_state = em,
         S7_housing_quality = hous,
         S7_neighbourhood_safety = safe) %>%

write.csv(df3, 
          file = '/home/luke/Documents/WORK/MINOS/EI_calc_prepared.csv')

```
